Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
asd
MAde some sense

\begin{table}
	\centering
	\begin{tabular}[ht]{| l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults  \\
	\hline
	Group A & 36 & 40 & 35 \\
	\hline
	Group B & 31 & 47 & 28 \\
	\hline
	\end{tabular}
	\caption{Fault frequency of risk type per group}
\end{table}

@@

As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar. Both show that there is a difference between the two inspection methods, and both show greater results for CL.

%% ctrl+F for "exactly  and why one inspection process"

@@

When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding. A suggestion for a follow up study would be to determine exactly  and why one inspection process finds them over the other.

>>>>

\begin{table}
	\centering
	\begin{tabular}[ht]{| l | l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults & Excluded\\
	\hline
	UC & 36 & 40 & 35 & 9\\
	\hline
	CL & 31 & 47 & 28 & 27\\
	\hline
	\end{tabular}
	\caption{Fault frequency of risk type per group}
\end{table}

@@

As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar. Both show that there is a difference between the two inspection methods, and both show greater results for CL. Table 3 shows that UC finds more faults of risk type A and C, but the fact that the CL data contained 18 more faults that contained an incorrect fault risk entry could be a possible explanation for that.

@@

When looking at the results of the study, UC appears to find many more class A and class B faults than CL, however, CL finds more class B faults. However, on average, the CL reviews found more faults overall and as such could be considered more effective than UC. This, coupled with the rejection of the H\textsubscript{Fault} null hypothesis, provides ample evidence that the review techniques do differ in which faults they are finding. A suggestion for a follow up study would be to determine why one inspection process finds faults that the other does not and if this affects the effectiveness of that process.
